\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures. \notaV{Index Structures (NOTE: WE NEED TO CHANGE THE NAME; Probably "Analytical model for porous silicon structures with 1D gradient refractive index"}}

### 2020-10-26 paper.tex

\title{\textbf{Optimization of Porous Silicon Gradient Refractive
    Index Structures.} }
\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

@@

\begin{abstract}
We propose a simple setup which that the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous Silicon structures with a controlled gradient in their
index of refraction. We produced samples under several conditions and
characterized them with scanning electron microscopy, and
ultraviolet-visible-near infrared reflectance spectroscopy. Our
results allow us to obtain from experiments on a single or just a few
samples a full characterization of the dependence of porosity,
dielectric function and speed of attack on the current density and on
position, so that novel nonhomogeneous devices may be designed and
built.
\notaV{ABSTRACT :  Surfaces with the gradient in the refractive index 
have attracted attention due to their ability to unpair the relation
 between the shape of the optical lens with its optical response. 
  For enhancing the versatility  of electrochemical gradients and its possible usage in
different kinds of devices and applications, it is
desirable to predesign GRIN structures with spatial 
predictability of porosity and the corresponding etching rate.  
In this work, we propose a simple model for the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous silicon structures with a controlled gradient in their
index of refraction. The characterization of some typical PS samples with 
lateral porosity and thickness gradient (produced using pin Pt electrode) 
with scanning electron microscopy and
ultraviolet-visible-near infrared reflectance spectroscopy was 
found to be in conformity with the properties predicted through 
the proposed model. In addition,
as the results allow us to obtain the complete dependence of
porosity, dielectric function and the corresponding etching rate for each 
current density from some measurements performed on a single or 
a couple of samples, the proposed model can facilitate the designing 
of novel sensing devices based on surfaces with lateral gradient in refractive indices.}
Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}

@@

Surfaces with gradient in the refractive index (GRIN) are of 

@@

engineer/tune the propagation of light within the structure’s 
surface for applications such as flat lenses, but also for several 

@@

Kruger et al showed the \cite{krueger2016porous}

@@

In addition the same group \cite{krueger2018electrochemical}
%[Krueger, Neil A., et al. 
% "Electrochemical Fabrication of Flat, Polymer‐Embedded 
%Porous Silicon 1D Gradient Refractive Index Microlens 
%Arrays." physica status solidi (a) 215.13 (2018): 1800088].  
Recently, J Wang et al. has shown the fabrication of 
miniature spectrometer with PS based rugate filter using 
radial interfacial potential distribution \cite{wang2019fabrication}
%(Wang, Joanna, 
%Michael J. Sailor, and Byoung‐Yong Chang. "Fabrication of a lateral 
%gradient rugate in porous silicon for a miniature spectrometer
%application." ChemElectroChem 6.24 (2019): 5967-5972.
On the other hand, the effect of different topographical
features present on the same chip, has also been 
used to culture / adhesion of certain cells \cite{khung2008using}
In the investigation of such practically applicable systems, 
the spacial predictability of electrochemical gradients can 
be useful for predesigning the devices for different applications.  
In this work, we report a simple analytical model to quantitatively 
analyze the gradient (calculate the porosity /current density and 
thickness) at any point of the GRIN structure.  The paper is organized 
as follows. In Section 2  we report a simple analytical model to calculate 
the current density/porosity and thickness  at any point of the GRIN structure. 
The model contemplates (Dr. Mochan) the formation of electrochemically generated 
porous surface  (applicable/extendible to photonic crystals with lateral gradient) 
with lateral gradient in refractive index  ...with predictable  depth and porosity 
at any point on surface.   In Section 3 we provide experimental details for the 
synthesis of porous silicon samples with lateral refractive index gradient.  
Section 4 includes experimental results and its comparison with numerically 
evaluated parameters. Finally,  the conclusions are given in Section 5
%$ 
%
}

>>>>

\title{\textbf{Optimization of Porous Silicon Gradient Refractive
    Index Structures. \notaV{Index Structures (NOTE: WE NEED TO CHANGE THE NAME;  
    Probably "Analytical model for  porous silicon structures with 1D gradient refractive index"}} }
\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

@@

\begin{abstract}
We propose a simple setup which that the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous Silicon structures with a controlled gradient in their
index of refraction. We produced samples under several conditions and
characterized them with scanning electron microscopy, and
ultraviolet-visible-near infrared reflectance spectroscopy. Our
results allow us to obtain from experiments on a single or just a few
samples a full characterization of the dependence of porosity,
dielectric function and speed of attack on the current density and on
position, so that novel nonhomogeneous devices may be designed and
built.
\notaV{Surfaces with  the gradient in the refractive index have 
attracted attention due to their capacity to unpair the relation 
between the shape of the optical 
lens with its optical response.  For enhancing the versatility  of 
electrochemical gradients and its possible usage in 
different kinds of devices and applications, it is
desirable to predesign GRIN structures with spatial predictability of 
porosity and the corresponding etching rate.  In this work, we propose a 
simple model for the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous silicon structures with a controlled gradient in their
index of refraction. The characterization of some typical PS samples with 
lateral porosity and thickness gradient (produced using pin Pt electrode) 
with scanning electron microscopy andultraviolet-visible-near infrared 
reflectance spectroscopy was found to be in conformity with the properties 
predicted through the proposed model. In addition, 
as the results allow us to obtain the complete dependence of porosity,
dielectric function and the corresponding etching rate for each current
density from some measurements performed on a single or a couple of samples,
the proposed model can facilitate the designing of novel sensing devices 
based on surfaces with lateral gradient in refractive indices.}
Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}

@@

Gradient in the refractive index (GRIN) of a material is of 

@@

engineer/tune the propagation of light within the structure for 
applications such as flat lenses, but also for several 

@@

Krueger et al. \cite{krueger2018electrochemical} in 2018 used porous 
silicon 1D GRIN structure 
infiltrated with polymer to synthesize flat microns arrays. 

@@

%[Krueger, Neil A., et al. 
% "Electrochemical Fabrication of Flat, Polymer‐Embedded 
%Porous Silicon 1D Gradient Refractive Index Microlens 
%Arrays." physica status solidi (a) 215.13 (2018): 1800088].  
Recently, J Wang et al. has shown the fabrication of 
miniature spectrometer with PS based rugate filter using 
radial interfacial potential distribution \cite{wang2019fabrication}
%(Wang, Joanna, 
%Michael J. Sailor, and Byoung‐Yong Chang. "Fabrication of a lateral 
%gradient rugate in porous silicon for a miniature spectrometer
%application." ChemElectroChem 6.24 (2019): 5967-5972.
On the other hand, the effect of different topographical
features present on the same chip, has also been 
used to culture / adhesion of certain cells \cite{khung2008using}
In the investigation of such practically applicable systems, 
the spacial predictability of electrochemical gradients can 
be useful for predesigning the devices for different applications.  
In this work, we report a simple analytical model to quantitatively 
analyze the gradient (calculate the porosity /current density and 
thickness) at any point of the GRIN structure.  The paper is organized 
as follows. In Section 2  we report a simple analytical model to calculate 
the current density/porosity and thickness  at any point of the GRIN structure. 
The model contemplates (Dr. Mochan) the formation of electrochemically generated 
porous surface  (applicable/extendible to photonic crystals with lateral gradient) 
with lateral gradient in refractive index  ...with predictable  depth and porosity 
at any point on surface.   In Section 3 we provide experimental details for the 
synthesis of porous silicon samples with lateral refractive index gradient.  
Section 4 includes experimental results and its comparison with numerically 
evaluated parameters. Finally,  the conclusions are given in Section 5
%$ 
%
}
